Risk Perceptions for Wearable Devices

### 2015-03-03 riskbenefit.tex
riskbenefit column fix
title

Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerRisk} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleBenefit} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunBenefit} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerBenefit} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityRisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleRisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunRisk} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityBenefit} \\ 
 & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tables/risk} & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tables/ben} \\ 
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

>>>>

Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerRisk}  & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerBenefit}\\

Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityBenefit}  \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleRisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleBenefit} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunRisk}& 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunBenefit}  \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}
